Computer Science House Constitution

### 2023-11-06 constitution.tex
Resolve #67 4.B.4 Remove Last Paragraph (#74)
* Remove voting exemption paragraph in 4.B.4

* Resolve changes to just those pertinent to the PR

---------

Co-authored-by: Sam-Cordry <samcordry@gmail.com>
Resolve #71 Condense Leave of Absence (#130)
* Codensed leave of absence

* Made requested changes

* Fixed formatting to be 1 sentence per line

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director. They will retain their previous Housing Status if applicable.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
If the vote passes the Alumni is reinstated as an Active Member effective immediately.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the privilege to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
Active Members currently on co-op forfeit their right to vote on house issues, and likewise do not count towards quorum.
Exceptions may be made at the discretion of the Evaluations Director.
\asubsection{Active Membership Evaluations}
Active Members are evaluated annually through the Evaluation Process as described in \ref{Evaluations Processes}.
\asubsection{Active Membership Leave of Absence}
An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}.
For the duration of an absence, a member:
\begin{itemize}
	\item Forfeits their right to vote
	\item Does not count towards quorum
	\item Will not be required to attend House Meeting
\end{itemize}
\asubsection{Active Membership Resignations}
An Active member may resign by submitting, in writing, the reason for resignation to the Chairperson, or Evaluations Director.
Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Active Membership Term}
Active Membership shall last until the member resigns or changes membership status.

@@

\asection{Leave of Absence}
A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
Computer Science House recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence.
House will also help to reacclimate any returning member back to the culture of House upon their return.
Upon approval of a leave of absence request, the Evaluations Director is notified and the member's leave is applied immediately.
A member is also allowed to be physically present and also be on a leave of absence.
\asubsection{Leave of Absence Request}
A leave of absence request must include the following information about the member: name, email, phone number, start date, expected return date, and a reason for the leave.
The request is then given to a staff member of Residence Life, excluding student employees, for approval.
A leave of absence start date can be backdated.
At no point does the Executive Board need to be informed of any details relating to the reason for the leave.
\asubsection{Leave of Absence Duration}
A leave of absence can be granted for up to the length of one semester.
\asubsection{Leave of Absence Extension}
A leave of absence can be extended by submitting a new request.
\asubsection{Leave of Absence Return}
A member may return from a leave of absence whenever they choose to.
When a member wishes to return, they must in writing notify a staff member of Residence Life, excluding student employees, to end their leave of absence.
\asubsection{Modified Evaluations}
A member may request their evaluation period to be extended by the duration of the leave or to end of the Standard Operating Session, whichever comes first.
\asubsection{Leave of Absence for an Executive Board Member}
The duties and responsibilities of an Executive Board Member on leave are assumed using the process defined in Section \ref{Appointment of an Interim Director} until the member returns from their leave.
Upon returning, the member may assume their position and the interim director is removed.
If at any point the member's leave is determined by the Executive Board to be detrimental to the operations of house, any Executive Board member may propose a two-thirds vote amongst the Executive Board to require a resignation from the Member.

>>>>

\asection{Active Membership}
\asubsection{Active Membership Qualifications}
Active Membership is open to all students currently enrolled at the Rochester Institute of Technology who have passed the Introductory Evaluation and their most recent Membership Evaluation.
\asubsection{Active Membership Selection}
Alumni Members in good standing may self-select into Active Membership by paying dues to the Financial Director and notifying the Evaluations Director. They will retain their previous Housing Status if applicable.
\\*\\*
Any Alumni Member in bad standing (\ref{Alumni Membership Selection}) may become an Active Member by notifying the Evaluations Director of their intent to participate, who will bring them up for a Simple Majority vote at the next House meeting.
If the vote passes the Alumni is reinstated as an Active Member effective immediately.
\asubsection{Active Membership Expectations}
Active members are expected to be active participants in the House as defined in \ref{Expectations of House Members}.
\asubsection{Active Membership Privileges}
Active Members receive the privilege to:
\begin{itemize}
	\item Vote on all issues brought before the House
	\item Reside on the House
	\item Hold an Executive Board office on the House
	\item Use Computer Science House facilities
	\item Attend Computer Science House functions
	\item Receive priority for available housing on the House when returning from cooperative education
	\item Guaranteed housing in compliance with the Residence Life policies regarding Special Interest Houses and the Housing Selection Process (if they have On-Floor status)
\end{itemize}
\asubsection{Active Membership Evaluations}
Active Members are evaluated annually through the Evaluation Process as described in \ref{Evaluations Processes}.
\asubsection{Active Membership Leave of Absence}
An Active member may at any time request a leave of absence using the process described in \ref{Leave of Absence}.
For the duration of an absence, a member:
\begin{itemize}
	\item Forfeits their right to vote
	\item Does not count towards quorum
	\item Will not be required to attend House Meeting
\end{itemize}
\asubsection{Active Membership Resignations}
An Active member may resign by submitting, in writing, the reason for resignation to the Chairperson, or Evaluations Director.
Instead of forfeiting membership, Active members who resign may elect to become Alumni defined in \ref{Alumni Membership Selection}.
The resignation will take effect immediately and an announcement will be made at the following House Meeting.
\asubsection{Active Membership Term}
Active Membership shall last until the member resigns or changes membership status.

@@

\asection{Leave of Absence}
A Leave of Absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member. 
In order to request a Leave of Absence, a member must follow the RIT policy for Leave of Absence, located at \url{https://www.rit.edu/policies/d021}. Additionally, the member should notify the Evaluations Director of their Leave, at which point they become exempt from all House requirements until they return.
